### 2023-06-13 paper/main.tex
..

>>>>

\begin{figure*}[h!]
    \begin{center}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_center.png}
            \footnotesize \put(0,2){(a)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_right.png}
            \footnotesize \put(0,2){(b)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_front.png}
            \footnotesize \put(0,2){(c)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
            \footnotesize \put(0,2){(d)}
        \end{overpic}\\
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_center.png}
            \footnotesize \put(0,2){(a)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_right.png}
            \footnotesize \put(0,2){(b)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/nara_front.png}
            \footnotesize \put(0,2){(c)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/firtha_back.png}
            \footnotesize \put(0,2){(d)}
        \end{overpic}\\
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_center.png}
            \footnotesize \put(0,2){(a)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_right.png}
            \footnotesize \put(0,2){(b)}
        \end{overpic}\hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
            \footnotesize \put(0,2){(c)}
        \end{overpic} \hspace{3mm}
        \begin{overpic}[width = 0.45\columnwidth]{figs/transfer_front.png}
            \footnotesize \put(0,2){(d)}
        \end{overpic}\\
    \end{center}
    \caption{fg}
    \label{Fig:aliasing}
\end{figure*}
